\documentclass[12pt,letterpaper]{article}
\title{HOUSE RULES} 
\author{Pittsburgh Association of the Deaf, Inc.}
\date{August 12, 2017}

\begin{document}
\maketitle

\begin{enumerate}
\item Members will be held responsible for the conduct of their guests.

\item Everyone must be a member to enter the premises. Everyone is required to
bring his/her membership card with him/her.

\item No alcoholic beverages shall be sold to non-members.

\item Members are required to identify themselves as members when requested to do
so by any member of the Board of Directors, the Club Manager or any Active
member.

\item All games in the clubroom shall be subject to such regulations as may be
imposed by the Board of Directors.

\item Nobody shall remove any property belonging to the club. Anyone who removes
the club’s property, or who mutilates or destroys any club property may be
cited before the Board of Directors in accordance with Article XII, Section 5 of
the Bylaws.

\item Boisterous or unseemly conduct or language in or about the club premises is
prohibited. An offending person may be liable for suspension or expulsion.

\item Special rules shall apply to the club barroom and social room as each occasion
requires.

\item Pets shall not be allowed in the club. Guide Dog for the blind, Service Dog for
the Deaf/Hard of Hearing or Therapy Dog for physically challenged person are
permitted.

\item The club shall not be responsible for personal property of its members and
guests.

\item Anyone under 21 years old shall not be permitted to sit at the bar.

\item Minors under age of 18 years old must evacuate the premises by midnight
unless accompanied by an adult or legal guardian or under proper supervision
of an adult, 25 years of age or older.

\item Children under 12 years old are not permitted in the club during the weekends
at any time EXCEPT during special events only.

\item No tank tops or sleeveless T-shirts shall be worn by male persons during any
events on Wednesdays, Fridays and Saturdays.

\item Notices may be placed on the bulletin board only by authority of a club officer
or the Club Manager.

\item All suggestions, requests and complaints with respect to club matters and
management shall be made in writing, signed by a member, and addressed to
the Board of Directors. All complaints concerning service and the conduct of
bartenders shall be made to the Club Manager or the Board of Directors.

\item ILLEGAL DRUGS OR WEAPONS are not permitted on the club’s premises at
any time. Those in possession or found responsible for bringing them into the
club or surrounding area of the club shall be subject to suspension for a period
of two years. An accused person may be suspended after a due process hearing
by a 2/3 vote of the Board of Directors. Reinstatement to membership must be
done in writing and voted upon by the Active members.

\end{enumerate}
\end{document}
